An Empirical Measurement-Based Analysis for Linux-based Real-Time Multiprocessor Scheduling

### 2017-04-21 paper.tex
Ready to submit

\title{Title}

\author{\IEEEauthorblockN{Ching-Chun (Jim) Huang} \IEEEauthorblockA{Department of\\Computer Science and Information
Engineering\\National Cheng Kung University, Taiwan\\ No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\ Email:
jserv@ccns.ncku.edu.tw} \and \IEEEauthorblockN{Chung-Fan Yang} \IEEEauthorblockA{Department of Electrical Engineering\\
National Cheng Kung University, Taiwan\\ No.1, University Road, Tainan City 701, Taiwan (R.O.C.)\\ Email:
E24026048@mail.ncku.edu.tw}}

@@

\begin{abstract}
\end{abstract}

@@

The processing of time-critical tasks, depends upon the capacity of the system to respond to an event, within
a known and bounded interval of time. Existing techniques for effectively scheduling real-time workloads on
multiprocessors has been increasing recently.

Two factors are driving this movement. First, algorithmic research on this topic has resulted in a number of new
scheduling approaches that remove some of the fundamental barriers imposed by partitioning approaches, the scheme
smost commonly considered in earlier work. Second, the landscape in terms of hardware platforms has been changing:
"server-class" multiprocessor machines have been availablefor some time now, and SoC vendors are shifting to
multi-core technologies as a solution to the "thermal roadblock" imposed by single-core designs. In multicore
platforms, several processor cores are placed on a single chip. Most major chip manufacturers currently offer
more core.

@@

\section{Conclusion}

    We have evaluated the real-time behavior of Linux by profiling kernel scheduler and measuring the latency of various
    kernel variants. An intensive interrupt load can cause long OS latencies due to the design of the interrupt
    processing mechanism. We proposed new tools to visualize task scheduling in fine-grained scale(microsecond level).
    This enabled us not only focusing on interrupt latency, but also scheduler durations, lock, and etc. It would thus
    be highly desirable to combine existing techniques, e.g KML, isolated CPU, tickless kernel, to improve task
    responsiveness under various target application characteristics, on top of PREEMPT\textunderscore RT.

>>>>

\title{An Empirical Measurement-Based Analysis for Linux-based Real-Time Multiprocessor Scheduling}

\author{\IEEEauthorblockN{Ching-Chun (Jim) Huang} \IEEEauthorblockA{Department of\\Computer Science and Information
Engineering\\National Cheng Kung University, Taiwan\\ No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}
\and \IEEEauthorblockN{Chung-Fan Yang} \IEEEauthorblockA{Department of Electrical Engineering\\
National Cheng Kung University, Taiwan\\ No.1, University Road, Tainan City 701, Taiwan (R.O.C.)}}

@@

\begin{abstract}
A real-time, Linux-based testbed, which we have developed for empirically evaluating multiprocessor
scheduling hehavior is presented, along with various enhancements that remove some of the fundamental
barriers to eliminate potential latency. Both raw performance and schedulability are considered for
hard real-time constraints. To our knowledge, this paper is the first attempt by anyone to obtain
comprehensive performance results regarding the scheduler and its interaction with external events.
\end{abstract}

@@

The processing of time-critical tasks, depends upon the capacity of the system to respond to an event, within
a known and bounded interval of time. We have constructed a set of system utilities as a testbed to discover
Linux scheduling, multi-core overhead and real-time performance from microscopic view.

The landscape in terms of hardware platforms has been changing: "server-class" multiprocessor machines have
been available for some time now, and SoC vendors are shifting to multi-core technologies as real-time system
solutions. Our goal was to produce a platform that supports both static and dynamic workloads for real-time constraints.

@@

\section{Conclusion}
    We have evaluated Linux real-time behavior by profiling kernel scheduler and measuring the latency.
    An intensive interrupt load can cause long OS latencies due to the design of the interrupt
    processing mechanism. We proposed new tools to visualize task scheduling in fine-grained scale(microsecond level).
    It encourages us to focus on not only interrupt latency but also scheduler durations, lock, etc., andt would thus
    be highly desirable to combine existing techniques, e.g isolated CPU, tickless kernel, to improve task responsiveness
    under various target application characteristics, with our testbed.
